Binary Latent Representations for Efficient Ranking

### 2017-06-05 paper/paper.tex
Add experimental setup section.

Note that the binary dot produt approach generalizes beyond simple factorization models, and can be applied as a component of any model whose final scoring step involves a dot product between user and item representations. In particular, models using recurrent \citep{hidasi2015session} or convolutional \citep{lynch2015images} item or user representations can easily be augmented to use binary dot products in the final ranking stages.

@@

\bibliographystyle{abbrv}
\bibliography{bibliography}

>>>>

Note that the binary dot produt approach generalizes beyond simple factorization models, and can be applied as a component of any model whose final scoring step involves a dot product between user and item representations. In particular, models using recurrent (like Session-based Recommendations with Recurrent Neural Networks) or convolutional (Images Don’t Lie: Transferring Deep Visual Semantic
Features to Large-Scale Multimodal Learning to Rank) item or user representations can easily be augmented to use binary dot products in the final ranking stages.

@@

%\bibliographystyle{abbrv}
%\bibliography{main}
